Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
pf <- read.csv("pseudo_facebook.tsv",sep='\t')
```

***

#### What are some things that you notice right away?
Response:

三十岁以下的人好友数较多

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point() + 
  xlim(13,90)

summary(pf$age)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_jitter(alpha = 1/20) + 
  xlim(13,90)
```

#### What do you notice in the plot?
Response:

从青年到中年，好友数减少。50岁左右，好友数会上升。

***

### Coord_trans()
Notes:

```{r Coord_trans()}
?coord_trans()
```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha = 1/20, position = position_jitter(h=0)) + 
  xlim(13,90) +
  coord_trans(y = "sqrt")
```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x = age, y = friendships_initiated), data = pf) + 
  geom_point(alpha = 1/10, position = position_jitter(h=0)) + 
  xlim(13,90) +
  coord_trans(y = "sqrt")
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
install.packages('dplyr')
library(dplyr)
```

```{r}
pf.fc_by_age <- pf %>%
  group_by(age) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age)
  
head(pf.fc_by_age)
```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(x = age, y = friend_count_mean), data = pf.fc_by_age) + 
  geom_line() + 
  xlim(13,90)
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha = 1/10, position = position_jitter(h=0), color ="orange") + 
  geom_line(stat = "summary", fun.y = mean) + 
  geom_line(stat = "summary", fun.y = quantile, fun.args = list(probs = .1),  linetype =2, color = "blue") +
    geom_line(stat = "summary", fun.y = quantile, fun.args = list(probs = .5),   color = "blue") +
  geom_line(stat = "summary", fun.y = quantile, fun.args = list(probs = .9),  linetype =2, color = "blue") +
  coord_cartesian(xlim = c(13, 70), ylim=c(0,1000)) 
```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
age <- pf$age
friend_count <- pf$friend_count
cor.test(age, friend_count,method = "pearson")
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

```{r}
?cor.test
```

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(pf, age <=70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
ggplot(aes(x = www_likes_received, y = likes_received), data = pf) + 
  geom_point() + 
  xlim(0,quantile(pf$www_likes_received, 0.95)) + 
  ylim(0,quantile(pf$likes_received, 0.95)) +
  geom_smooth(method='lm', color = 'red')
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
www_likes_received <- pf$www_likes_received
likes_received <- pf$likes_received
cor.test(www_likes_received, likes_received,method = "pearson")
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```
```{r}
data(Mitchell)
?Mitchell
head(Mitchell)
```

Create your plot!

```{r Temp vs Month}
ggplot(aes(x = Month, y = Temp), data = Mitchell) + 
  geom_point() 
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

0

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

0.057

```{r Noisy Scatterplots}
month <- Mitchell$Month
temp <- Mitchell$Temp
cor.test(x = month, y = temp, Method=c("pearson"))
```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
ggplot(data = Mitchell, aes(x = Month, y = Temp)) + 
  geom_point() +
  scale_x_continuous(breaks = seq(0,203,12))
```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
ggplot(aes(x = age, y = friend_count_mean), data = pf.fc_by_age) + 
  geom_line() 
```

***

### Age with Months Means

```{r Age with Months Means}
pf$age_with_months <- pf$age + (1 - pf$dob_month / 12) 


```

Programming Assignment
```{r Programming Assignment}
pf.fc_by_age_with_months <- pf %>%
  group_by(age_with_months) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age_with_months)
  
head(pf.fc_by_age_with_months)
```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}
ggplot(aes(x = age_with_months, y = friend_count_mean), data = pf.fc_by_age_with_months) + 
  geom_line() + 
  xlim(0,70) +
  ylim(0,450)
```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}
p1 <- ggplot(aes(x = age, y = friend_count_mean), data = pf.fc_by_age) + 
  geom_line() +
  xlim(0,70) +
  ylim(0,450) +
  geom_smooth()

p2 <- ggplot(aes(x = age_with_months, y = friend_count_mean), data = pf.fc_by_age_with_months) + 
  geom_line() + 
  xlim(0,70) +
  ylim(0,450) +
  geom_smooth()

p3 <- ggplot(aes(x = round(age / 5) * 5, y = friend_count), data = subset(pf, age < 71)) + 
  geom_line(stat='summary', fun.y=mean) 
  
library(gridExtra)
grid.arrange(p1,p2,p3,ncol=1)
```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

